### 2016-03-29 WRITEUP/Lensmodel.tex
table report magnification factors across channels

\documentclass[]{emulateapj}
\usepackage{amsmath}
\begin{document}
\author{Draft}

@@

>>>>

\documentclass[]{emulateapj}
\usepackage{amsmath}
\input{preamble}
\begin{document}
\author{Draft}

@@

%%%%%%%%%%%%%%%%%%%%%%%%
+ Compare our lens model parameters on the mass distribution of the lensing
galaxy with literature (specifically SIE model in C06)
	- C06: SIE model shows position of lensing mass is offset by (-0.015",
-0.041" from obs. (i.e. light centroid)); PA = -73.6, ellipticity = 0.45,
theta\_R = 1.84" $\pm$ 0.01 
	- Our model lens parameters (median):
		- file: WRITEUP/MedianLensModelParams.txt
		- lensing gal. position is consistent with C06, 
		- Einstein radius: consistent with C06
		- PA: consistent within errors
		- Axial ratio: consistent within errors
%%%%%%%%%%%%%%%%%%%%%%%%%

\input{table_magFactor}
